On the Functionality of the Multilayer Perceptron

### 2020-09-29 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Thesis Draft v0

% ================================================================
% ================================================================
\newpage
\section{Methodology}
\label{sec-Methodology}

@@

>>>>

\newpage
\section{Methodology}
\label{sec-Methodology}

@@

\newpage
\section{Experimental Results}
\label{sec-Results}

\newpage
\section{Conclusion}
\label{sec-Conclusion}

\newpage
\section{Acknowledgments}
\label{sec-Acknowledge}

\paragraph*{}The completion of this project would not have been possible without the various contributions from the following people:

\begin{itemize}

\item[•]Nathan Richard for consultation on physics, mathematics, and programming topics.

\item[•]Morgan Saidel for consultation on physics, mathematics, and programming topics.

\item[•]Madeline Edwards for differing me to this project, as well as constant support and consultation on mathematical topics.

\item[•]John Parker for consultation on physics, mathematics, and programming topics.

\item[•]Dakota Buell for consultation on physics, mathematics, and programming topics.

\item[•]Dr. Kevin Short for various consultation and guidence throughout this project

\item[•]Dr. Maurik Holtrop for various consultation and guidence throughout this project

\end{itemize}
